Panel Seminars

### 2023-02-08 index.Rmd
changes to yml and index for rda tutorial

* [Choosing a population genomics sequencing approach](choosing-population-genetics.html)  
* [Whole Genome Resequencing (WGS)](WGS_intro.html)  
  * [Low coverage WGS](https://github.com/therkildsen-lab/genomic-data-analysis/blob/master/lcwgs_data_analysis.md)
* [Reduced Representation Sequencing](RADseq.html) 
* [Poolseq](poolseq.html)

>>>>

* [Choosing a population genomics sequencing approach](choosing-population-genetics.html)  
* [Whole Genome Resequencing (WGS)](WGS_intro.html)  
  * [Low coverage WGS](https://github.com/therkildsen-lab/genomic-data-analysis/blob/master/lcwgs_data_analysis.md)
* [Reduced Representation Sequencing](RADseq.html) 
* [Poolseq](poolseq.html)
* [Redundancy Analysis (RDA) Trait Prediction](RDAtraitPredictionTutorial.html)
